Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-28 analysis/study2.qmd
Update study2.qmd

data <- rbind(
  data,
  pool_coef(with = "NEO_FFI_Mean", component = "Personality", name = "Neuroticism"),
  pool_coef(with = "BFI_AGREEABLENESS", component="Personality", name = "Agreeableness"),
  pool_coef(with = "BFI_CONSCIENTIOUSNESS", component="Personality", name = "Conscientiousness"), 
  pool_coef(with = "BFI_NEUROTICISM", component="Personality", name = "Neuroticism"),
  pool_coef(with = "BFI_OPENNESS", component="Personality", name = "Openness"),
  pool_coef(with = "BFI_EXTROVERSION", component="Personality", name = "Extraversion"),
  pool_coef(with = "IPIP6_Agreeableness", component="Personality", name = "Agreeableness"),
  pool_coef(with = "IPIP6_Conscientiousness", component="Personality", name = "Conscientiousness"), 
  pool_coef(with = "IPIP6_Neuroticism", component="Personality", name = "Neuroticism"),
  pool_coef(with = "IPIP6_Openness", component="Personality", name = "Openness"),
  pool_coef(with = "IPIP6_Extraversion", component="Personality", name = "Extraversion"), 
  pool_coef(with = "IPIP6_HonestyHumility", component="Personality", name = "Honesty-Humility")
)
```

>>>>

data <- rbind(
  data,
  pool_coef(with = "Neuroticism", component = "Personality", name = "Neuroticism"),
  pool_coef(with = "Agreeableness", component="Personality", name = "Agreeableness"),
  pool_coef(with = "Conscientiousness", component="Personality", name = "Conscientiousness"), 
  pool_coef(with = "Openness", component="Personality", name = "Openness"),
  pool_coef(with = "Extraversion", component="Personality", name = "Extraversion"),
  pool_coef(with = "HonestyHumility", component="Personality", name = "Honesty-Humility")
)
```
